A Horrocks-type theorem for even orthogonal $K_2$

### 2019-09-26 dl-paper.tex
Minor

\begin{lemma}\label{P0_conj} The subgroup $P_\alpha(0)$ is stable under conjugation by $x_\alpha(aX^{-1})$ for arbitrary $a\in A$. \end{lemma}
\begin{proof} We need to verify that the conjugate by $x_\alpha(aX^{-1})$ to every generator $g = z_\beta(f, \xi)$ from~\cref{defP0} lies in $P_\alpha(0)$. 
The assertion is clear for generators of type 3 and 5.
First of all, consider the case $\alpha + \beta \in \Phi$, which is only possible in the case of a generator of type 1:
\begin{equation}\label{eq:Zconj1} z_{\beta}(Xf, \xi) ^ {x_{\alpha}(aX^{-1})} = x_{\alpha} (- afg) \cdot x_{\alpha+\beta} (N_{\beta, \alpha}\cdot af) \cdot z_{\beta}(Xf, \xi). \end{equation}
Clearly, the expression in the right-hand side is a product of generators of type 5, 2, 1.

>>>>

\begin{lemma}\label{P0_conj} The subgroup $P_\alpha(0)$ is stable under conjugation by $x_\alpha(aX^{-1})$ for arbitrary $a\in A$. \end{lemma}
\begin{proof} We need to verify that the conjugate by $x_\alpha(aX^{-1})$ to every generator $g = z_\beta(f, \xi)$ from~\cref{defP0} lies in $P_\alpha(0)$. 
The assertion is clear for generators of type 3 and 5.
First of all, consider the case $\alpha + \beta \in \Phi$, which is only possible in the case of a generator of type 1:
\begin{equation}\label{eq:Zconj1} z_{\beta}(Xf, \xi) ^ {x_{\alpha}(aX^{-1})} = x_{\alpha} (- af\xi) \cdot x_{\alpha+\beta} (N_{\beta, \alpha}\cdot af) \cdot z_{\beta}(Xf, \xi). \end{equation}
Clearly, the expression in the right-hand side is a product of generators of type 5, 2, 1.
